---
title: "Learning Survey"
author: "Sizheng Zhu"
date: "11/29/2018"
output: html_document
---

##install
install.packages("readxl")
install.packages("dplyr")
install.packages("car")
install.packages("shiny")
install.packages("rsconnect")
## Data Manipulation

Reshape the dataset in Excel or R : 
Variables in the column should be the survey questions (i.e. field “SurveyQuestions_code” or field “SurveyQuestions_name”) with survey results (i.e. field “LearningSurvey_number_value”). 
Row should be the student record (i.e. total number of 208 students).
Rename the variables : 
From each question into “Survey_Question1”, “Survey_Question2”, …, “Survey_Question10”.

```{r}
library(readxl)
LS <- read_excel("~/Downloads/Learning Survey.xlsx")
View(LS)

library(dplyr)

LS <- select(LS,13,7,3)


LSQ1<- filter(LS, SurveyQuestions__code == "TC1")
LSQ1<- select(LSQ1,1,3)
names(LSQ1)<- c("student_id","Survey_Question1")

LSQ2<- filter(LS, SurveyQuestions__code == "TC2")
LSQ2<- select(LSQ2,1,3)
names(LSQ2)<- c("student_id","Survey_Question2")

LSQ3<- filter(LS, SurveyQuestions__code == "TC3")
LSQ3<- select(LSQ3,1,3)
names(LSQ3)<- c("student_id","Survey_Question3")

LSQ4<- filter(LS, SurveyQuestions__code == "TC4")
LSQ4<- select(LSQ4,1,3)
names(LSQ4)<- c("student_id","Survey_Question4")

LSQ5<- filter(LS, SurveyQuestions__code == "TC5")
LSQ5<- select(LSQ5,1,3)
names(LSQ5)<- c("student_id","Survey_Question5")

LSQ6<- filter(LS, SurveyQuestions__code == "TC6")
LSQ6<- select(LSQ6,1,3)
names(LSQ6)<- c("student_id","Survey_Question6")

LSQ7<- filter(LS, SurveyQuestions__code == "TC7")
LSQ7<- select(LSQ7,1,3)
names(LSQ7)<- c("student_id","Survey_Question7")

LSQ8<- filter(LS, SurveyQuestions__code == "TC8")
LSQ8<- select(LSQ8,1,3)
names(LSQ8)<- c("student_id","Survey_Question8")

LSQ9<- filter(LS, SurveyQuestions__code == "TC9")
LSQ9<- select(LSQ9,1,3)
names(LSQ9)<- c("student_id","Survey_Question9")

LSQ10<- filter(LS, SurveyQuestions__code == "TC10")
LSQ10<- select(LSQ10,1,3)
names(LSQ10)<- c("student_id","Survey_Question10")


library(plyr)
LSALL<- join_all(list(LSQ1,LSQ2,LSQ3,LSQ4,LSQ5,LSQ6,LSQ7,LSQ8,LSQ9,LSQ10), by= "student_id")

```
Rename the value labels into followings referring the code book : 
e.g. Change the “LearningSurvey_number_value = 99” into “Grade 2”. 
Eventually, all the data will be categorical data except Survey Question 10.
```{r}
LSALL$Survey_Question2[LSALL$Survey_Question2 == 96]<- "Male"
LSALL$Survey_Question2[LSALL$Survey_Question2 == 97]<- "Female"
LSALL$Survey_Question3[LSALL$Survey_Question3 == 98]<- "Grade 1"
LSALL$Survey_Question3[LSALL$Survey_Question3 == 99]<- "Grade 2"
LSALL$Survey_Question3[LSALL$Survey_Question3 == 100]<- "Grade 3"
LSALL$Survey_Question3[LSALL$Survey_Question3 == 101]<- "Grade 4"
LSALL$Survey_Question3[LSALL$Survey_Question3 == 102]<- "Grade 5"
LSALL$Survey_Question3[LSALL$Survey_Question3 == 103]<- "Grade 6"
LSALL$Survey_Question4[LSALL$Survey_Question4 == 106]<- "1.Advanced"
LSALL$Survey_Question4[LSALL$Survey_Question4 == 105]<- "2.Intermediate"
LSALL$Survey_Question4[LSALL$Survey_Question4 == 104]<- "3.Beginner"
LSALL$Survey_Question5[LSALL$Survey_Question5 == 107]<- "1.Once a week"
LSALL$Survey_Question5[LSALL$Survey_Question5 == 108]<- "2.Once every two weeks"
LSALL$Survey_Question5[LSALL$Survey_Question5 == 109]<- "3.Once a month"
LSALL$Survey_Question5[LSALL$Survey_Question5 == 110]<- "4.Once every two months"
LSALL$Survey_Question5[LSALL$Survey_Question5 == 111]<- "5.Never or almost never"
LSALL$Survey_Question6[LSALL$Survey_Question6 == 112]<- "1.High"
LSALL$Survey_Question6[LSALL$Survey_Question6 == 113]<- "2.Middle"
LSALL$Survey_Question6[LSALL$Survey_Question6 == 114]<- "3.Low"
LSALL$Survey_Question7[LSALL$Survey_Question7 == 115]<- "1.Never"
LSALL$Survey_Question7[LSALL$Survey_Question7 == 116]<- "2.1-30 minutes"
LSALL$Survey_Question7[LSALL$Survey_Question7 == 117]<- "3.30-60 minutes"
LSALL$Survey_Question7[LSALL$Survey_Question7 == 118]<- "4.60-90 minutes"
LSALL$Survey_Question7[LSALL$Survey_Question7 == 119]<- "5.More than 90 minutes"
LSALL$Survey_Question8[LSALL$Survey_Question8 == 120]<- "Yes"
LSALL$Survey_Question8[LSALL$Survey_Question8 == 121]<- "No"
LSALL$Survey_Question9[LSALL$Survey_Question9 == 122]<- "1.Never attended"
LSALL$Survey_Question9[LSALL$Survey_Question9 == 123]<- "2.Less than equal to 3 months"
LSALL$Survey_Question9[LSALL$Survey_Question9 == 124]<- "3.4-6 months"
LSALL$Survey_Question9[LSALL$Survey_Question9 == 125]<- "4.7-9 months"
LSALL$Survey_Question9[LSALL$Survey_Question9 == 126]<- "5.More than equal to 10 months"

```



## Descriptive Statistics in R

Generate frequency table for each survey question (Q1-Q9) and plot into bar chart.
```{r}
#Q1
ft1<-ftable(LSALL$Survey_Question1)
ft1_table<-as.data.frame(ft1)
names(ft1_table)<-c("Age","Frequency")

ft1_bar<-barplot(ft1, main="Question 1",
        names.arg=c(ft1_table$Age),
        xlab = "Age",
        ylab = "Frequency")

#Q2
ft2<-ftable(LSALL$Survey_Question2)
ft2_table<-as.data.frame(ft2)
names(ft2_table)<-c("Gender","Frequency")

ft2_bar<-barplot(ft2, main="Question 2",
        names.arg=c("Female","Male"),
        xlab = "Gender",
        ylab = "Frequency")

#Q3
ft3<-ftable(LSALL$Survey_Question3)
ft3_table<-as.data.frame(ft3)
names(ft3_table)<-c("Grade","Frequency")

ft3_bar<-barplot(ft3, main="Question 3",
        names.arg=c("Grade 1", "Grade 2", "Grade 3", "Grade 4", "Grade 5", "Grade 6"),
        xlab = "Grade",
        ylab = "Frequency")

#Q4
ft4<-ftable(LSALL$Survey_Question4)
ft4_table<-as.data.frame(ft4)
names(ft4_table)<-c("Math Level","Frequency")

ft4_bar<-barplot(ft4, main="Question 4",
        names.arg=c("Advanced","Intermediate","Beginner"),
        xlab = "Math Level",
        ylab = "Frequency")

#Q5
ft5<-ftable(LSALL$Survey_Question5)
ft5_table<-as.data.frame(ft5)
names(ft5_table)<-c("Absence","Frequency")

ft5_bar<-barplot(ft5, main="Question 5",
        names.arg=c("Once a week","Once every two weeks","Once a month","Once every two months","Never or almost never"),
        xlab = "Absence",
        ylab = "Frequency")

#Q6
ft6<-ftable(LSALL$Survey_Question6)
ft6_table<-as.data.frame(ft6)
names(ft6_table)<-c("SES","Frequency")

ft6_bar<-barplot(ft6, main="Question 6",
        names.arg=c("High","Middle","Low"),
        xlab = "SES",
        ylab = "Frequency")

#Q7
ft7<-ftable(LSALL$Survey_Question7)
ft7_table<-as.data.frame(ft7)
names(ft7_table)<-c("Homework","Frequency")

ft7_bar<-barplot(ft7, main="Question 7",
        names.arg=c("Never","1-30 minutes","30-60 minutes", "60-90 minutes","More than 90 minutes"),
        xlab = "Homework",
        ylab = "Frequency")

#Q8
ft8<-ftable(LSALL$Survey_Question8)
ft8_table<-as.data.frame(ft8)
names(ft8_table)<-c("Extra Math Class","Frequency")

ft8_bar<-barplot(ft8, main="Question 8",
        names.arg=c("No","Yes"),
        xlab = "Extra Math Class",
        ylab = "Frequency")

#Q9
ft9<-ftable(LSALL$Survey_Question9)
ft9_table<-as.data.frame(ft9)
names(ft9_table)<-c("Months(Extra Math Class)","Frequency")

ft9_bar<-barplot(ft9, main="Question 9",
        names.arg=c("Never attended","Less than equal to 3 months","4-6 months","7-9 months","More than equal to 10 months"),
        xlab = "Months(Extra Math Class)",
        ylab = "Frequency")


```
Produce summary statistics (i.e. mean, median, variance, standard deviation, max, min, range, quantile, mode) for variable “Survey_Question10”.
```{r}

first_qu <- as.data.frame(quantile(LSALL$Survey_Question10, 0.25))
     third_qu <- as.data.frame(quantile(LSALL$Survey_Question10, 0.75))
                
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

ss10 <- do.call(data.frame, 
           list(mean = mean(LSALL$Survey_Question10),
                median = median(LSALL$Survey_Question10),
                variance = var(LSALL$Survey_Question10),
                sd = sd(LSALL$Survey_Question10),
                max = max(LSALL$Survey_Question10),
                min = min(LSALL$Survey_Question10),
                range = max(LSALL$Survey_Question10)-min(LSALL$Survey_Question10),
                first_qu = first_qu$`quantile(LSALL$Survey_Question10, 0.25)`,
                third_qu = third_qu$`quantile(LSALL$Survey_Question10, 0.75)`,
                mode = Mode(LSALL$Survey_Question10)))
                
```
Assess the normality of the distribution of “Survey_Question10” (i.e. final score) using normal Q-Q plot. 
```{r}
library(car)
qqPlot(LSALL$Survey_Question10,main = "Q-Q Plot", ylab = "final score")

```
Create a box plot with “Survey_Question10” (i.e. final score) to see the values and outliers. 
```{r}
boxplot(LSALL$Survey_Question10, main="Final score", ylab="final score")


```
Perform one-way ANOVA test to find the relationship between two variables (categorical vs numerical).
Survey_Question2 vs Survey_Question10
Survey_Question3 vs Survey_Question10
Survey_Question4 vs Survey_Question10
Survey_Question5 vs Survey_Question10
Survey_Question6 vs Survey_Question10
Survey_Question7 vs Survey_Question10
Survey_Question8 vs Survey_Question10
Survey_Question9 vs Survey_Question10
```{r}
#Survey_Question2 vs Survey_Question10
aov2 <- aov(LSALL$Survey_Question10 ~ LSALL$Survey_Question2)
summary(aov2)
#Survey_Question3 vs Survey_Question10
aov3 <- aov(LSALL$Survey_Question10 ~ LSALL$Survey_Question3)
summary(aov3)
#Survey_Question4 vs Survey_Question10
aov4 <- aov(LSALL$Survey_Question10 ~ LSALL$Survey_Question4)
summary(aov4)
#Survey_Question5 vs Survey_Question10
aov5 <- aov(LSALL$Survey_Question10 ~ LSALL$Survey_Question5)
summary(aov5)
#Survey_Question6 vs Survey_Question10
aov6 <- aov(LSALL$Survey_Question10 ~ LSALL$Survey_Question6)
summary(aov6)
#Survey_Question7 vs Survey_Question10
aov7 <- aov(LSALL$Survey_Question10 ~ LSALL$Survey_Question7)
summary(aov7)
#Survey_Question8 vs Survey_Question10
aov8 <- aov(LSALL$Survey_Question10 ~ LSALL$Survey_Question8)
summary(aov8)
#Survey_Question9 vs Survey_Question10
aov9 <- aov(LSALL$Survey_Question10 ~ LSALL$Survey_Question9)
summary(aov9)

```
Perform Chi-Square test to find the relationship between two categorical variables. 
Rename the value labels of variable “Survey_Question10” into followings (i.e. categorical data).
Score 90-100: A
Score 80-90: B
Score 70-80: C
Score 60-70: D
Score under 60: F
```{r}
LSALL2<-LSALL

LSALL2$Survey_Question10[LSALL$Survey_Question10 >= 90 ]<- "A"
LSALL2$Survey_Question10[LSALL$Survey_Question10 >= 80 & LSALL$Survey_Question10 < 90  ]<- "B"
LSALL2$Survey_Question10[LSALL$Survey_Question10 >= 70 & LSALL$Survey_Question10 < 80]<- "C"
LSALL2$Survey_Question10[LSALL$Survey_Question10 >= 60 & LSALL$Survey_Question10 < 70 ]<- "D"
LSALL2$Survey_Question10[LSALL$Survey_Question10 < 60 ]<- "F"


chisq2<-chisq.test(LSALL2$Survey_Question2,LSALL2$Survey_Question10)
chisq3<-chisq.test(LSALL2$Survey_Question3,LSALL2$Survey_Question10)
chisq4<-chisq.test(LSALL2$Survey_Question4,LSALL2$Survey_Question10)
chisq5<-chisq.test(LSALL2$Survey_Question5,LSALL2$Survey_Question10)
chisq6<-chisq.test(LSALL2$Survey_Question6,LSALL2$Survey_Question10)
chisq7<-chisq.test(LSALL2$Survey_Question7,LSALL2$Survey_Question10)
chisq8<-chisq.test(LSALL2$Survey_Question8,LSALL2$Survey_Question10)
chisq9<-chisq.test(LSALL2$Survey_Question9,LSALL2$Survey_Question10)

```
Test the correlation between following two numerical variables and generate scatter plot. 
Survey_Question1 vs Survey_Question10
```{r}
plot(LSALL$Survey_Question1, LSALL$Survey_Question10, main="Q1", 
  	xlab="Age", ylab="Score")
# regression line (y~x)
abline(lm(LSALL$Survey_Question10~LSALL$Survey_Question1), col="red") 
# lowess line (x,y)
lines(lowess(LSALL$Survey_Question1,LSALL$Survey_Question10), col="blue") 


cor1<-cor(LSALL$Survey_Question1, LSALL$Survey_Question10)






```
Run the Linear Regression model with independent variable (Survey_Question1) and dependent variable (Survey_Question10). 
```{r}


linearMod <- lm(LSALL$Survey_Question1 ~ LSALL$Survey_Question10, data=LSALL)  
print(linearMod)


```

##Shiny Dashboard
Bar chart for “Survey Question 5” & Normal Q-Q plot for “Survey Question 10”

```{r}

library(shiny)
#Bar chart for “Survey Question 5” and “Survey Question 10 (categorical)”

ft5<-ftable(LSALL$Survey_Question5)
ft5_table<-as.data.frame(ft5)
names(ft5_table)<-c("Absence","Frequency")

LS_A<-filter(LSALL2, LSALL2$Survey_Question10 == "A")

A<-ftable(LS_A$Survey_Question5)
A_table<-as.data.frame(A)
names(A_table)<-c("Absence","A")

LS_B<-filter(LSALL2, LSALL2$Survey_Question10 == "B")

B<-ftable(LS_B$Survey_Question5)
B_table<-as.data.frame(B)
names(B_table)<-c("Absence","B")

LS_C<-filter(LSALL2, LSALL2$Survey_Question10 == "C")

C<-ftable(LS_C$Survey_Question5)
C_table<-as.data.frame(C)
names(C_table)<-c("Absence","C")

LS_D<-filter(LSALL2, LSALL2$Survey_Question10 == "D")

D<-ftable(LS_D$Survey_Question5)
D_table<-as.data.frame(D)
names(D_table)<-c("Absence","D")

LS_F<-filter(LSALL2, LSALL2$Survey_Question10 == "F")

F_<-ftable(LS_F$Survey_Question5)
F_table<-as.data.frame(F_)
names(F_table)<-c("Absence","F")


table5_10<-join_all(list(A_table,B_table,C_table,D_table,F_table), by= "Absence")

table5_10[is.na(table5_10)] <- 0

rownames(table5_10) <- table5_10[,1]
table5_10 <- table5_10[,-1]



# Use a fluid Bootstrap layout
ui1 <- fluidPage(    
  
  # Give the page a title
  titlePanel("Absence by score"),
  
  # Generate a row with a sidebar
  sidebarLayout(      
    
    # Define the sidebar with one input
    sidebarPanel(
      selectInput("score", "Final Score:", 
                  choices=colnames(table5_10)),
      hr()
    ),
    
    # Create a spot for the barplot
    mainPanel(
      plotOutput("absencePlot")  
    )
    
  )
)

server1 <- function(input, output) {
  
  # Fill in the spot we created for a plot
  output$absencePlot <- renderPlot({
    
    # Render a barplot
    barplot(table5_10[,input$score], 
            main=input$score,
            names.arg=c("Once a week","Once every two weeks","Once a month","Once every two months","Never or almost never"),
            ylab="Number of Students",
            xlab="Freqence",
            col = "light blue")
  })
}

shinyApp(ui = ui1, server = server1)

#Normal Q-Q plot for “Survey Question 10”

score_male<-filter(LSALL,LSALL$Survey_Question2 == "Male")
score_female<-filter(LSALL,LSALL$Survey_Question2 == "Female")

table_mf<-merge(score_male$Survey_Question10,score_female$Survey_Question10,by = 0, all = TRUE)[-1]
table_mf<-merge(table_mf,LSALL$Survey_Question10,by = 0, all = TRUE)[-1]
names(table_mf)<-c("Male","Female","Total")



ui2 <- fluidPage(    
  
  # Give the page a title
  titlePanel("Q-Q Plot by Gender"),
  
  # Generate a row with a sidebar
  sidebarLayout(      
    
    # Define the sidebar with one input
    sidebarPanel(
      selectInput("gender", "Gender:", 
                  choices=colnames(table_mf)),
      hr()
    ),
    
    # Create a spot for the qqplot
    mainPanel(
      plotOutput("QQPlot")  
    )
    
  )
)

server2 <- function(input, output) {
  
  # Fill in the spot we created for a plot
  output$QQPlot <- renderPlot({
    
    # Render a  Q-Q plot
    qqPlot(table_mf[,input$gender], 
            main=input$gender,
            ylab="final score")
  })
}

shinyApp(ui = ui2, server = server2)




#Two graphs in one page

ui3 <- fluidPage(    
  
  # Give the page a title
  titlePanel("Absence by score/Q-Q Plot by Gender"),
  # Generate a row with a sidebar
  sidebarLayout(   
    
    # Define the sidebar with one input
    sidebarPanel(
      selectInput("score", "Final Score:", 
                  choices=colnames(table5_10)),
      hr()
    ),
  sidebarLayout(  
    
    # Define the sidebar with one input
    sidebarPanel(
       selectInput("gender", "Gender:", 
                  choices=colnames(table_mf)),
      hr()
    ),

    
    # Create a spot for the barplot
    mainPanel(
      plotOutput("absencePlot"),
      plotOutput("QQPlot") 
    )
    
  )
)
)

server3 <- function(input, output) {
  
  # Fill in the spot we created for a plot
  output$absencePlot <- renderPlot({
    
    # Render a barplot
    barplot(table5_10[,input$score], 
            main=input$score,
            names.arg=c("Once a week","Once every two weeks","Once a month","Once every two months","Never or almost never"),
            ylab="Number of Students",
            xlab="Freqence",
            col = "light blue")
  })
    output$QQPlot <- renderPlot({
    
    # Render a  Q-Q plot
    qqPlot(table_mf[,input$gender], 
            main=input$gender,
            ylab="final score")
  })
}
shinyApp(ui = ui3, server = server3)



# Navbar Pages
ui4 <- navbarPage("Learning Survey",
  tabPanel("Absence by Score", 
    sidebarLayout(      
    
    # Define the sidebar with one input
    sidebarPanel(
      selectInput("score", "Final Score:", 
                  choices=colnames(table5_10)),
      hr()
    ),
    
    # Create a spot for the barplot
    mainPanel(
      plotOutput("absencePlot")  
    )
    )
           ),
  
  tabPanel("Q-Q Plot by Gender", sidebarLayout(      
    
    # Define the sidebar with one input
    sidebarPanel(
      selectInput("gender", "Gender:", 
                  choices=colnames(table_mf)),
      hr()
    ),
    
    # Create a spot for the qqplot
    mainPanel(
      plotOutput("QQPlot")  
    )
    
  )
           )
  
)


server4 <- function(input, output) {
  
  # Fill in the spot we created for a plot
  output$absencePlot <- renderPlot({
    
    # Render a barplot
    barplot(table5_10[,input$score], 
            main=input$score,
            names.arg=c("Once a week","Once every two weeks","Once a month","Once every two months","Never or almost never"),
            ylab="Number of Students",
            xlab="Freqence",
            col = "light blue")
  })
    output$QQPlot <- renderPlot({
    
    # Render a  Q-Q plot
    qqPlot(table_mf[,input$gender], 
            main=input$gender,
            ylab="final score")
  })
}
shinyApp(ui = ui4, server = server4)



library(rsconnect)

rsconnect::setAccountInfo(name='sizhengzhu',
			  token='C691303E0FD828D6A0B6240A24C05165',
			  secret='llJpGpB1tmuHUsWKa11ig7NxBSERmPAeYvF8IJ2k')

rsconnect::deployApp('path/to/your/app')

```





